A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-02-09 CWP/papers/HSF-CWP-2017-01_roadmap/latex/authors.tex
Update for arxiv v3 (#46)
* Updated author file

Add new author (Sunander) and correct place where footnote was for a few
of the Fermilab authors
Add a little more debug information when script has a problem
Regenerated tex file copied to CWP latex directory

* Update CMS figures

Correct error where MHS06s should be THS06s
Use PDFs instead of PNGs for improved quality

Anh-Ky, Nguyen$^{117}$;

@@

Bagliesi, Giuseppe$^{31}$;

@@

@@

Bauerdick, Lothar A. T.$^{16,c}$;
Belforte, Stefano$^{34}$;

@@

Boccali, Tommaso$^{31}$;

@@

Bonacorsi, Daniele$^{25}$;

@@

Bozzi, Concezio$^{27}$;

@@

Canal, Philippe$^{16,c}$;

@@

Carlino, Gianpaolo$^{30}$;

@@

@@

Chen, Gang$^{23}$;

@@

@@

Costanzo, Davide$^{108}$;

@@

Cristella, Leonardo$^{26}$;

@@

De, Kaushik$^{110}$;

@@

@@

@@

Dykstra, Dave$^{16,c}$;

@@

Elvira, V. Daniel$^{16,c}$;

@@

@@

Fitzpatrick, Conor$^{14}$;
Flix, José$^{57,7,g}$;

@@

@@

Gaede, Frank$^{13}$;

@@

Gellrich, Andreas$^{13}$;
Genser, Krzysztof$^{16,c}$;

@@

Giacomini, Francesco$^{9}$;
Giagu, Stefano$^{106,33}$;

@@

Glushkov, Ivan$^{110}$;

@@

Govi, Giacomo$^{16}$;
Grandi, Claudio$^{25}$;

@@

Guan, Wen$^{115}$;
Gutsche, Oliver$^{16,c}$;

@@

Hartmann, Thomas$^{13}$;

@@

Heinemann, Beate$^{13}$;

@@

Hernández, José M.$^{7,g}$;

@@

Hodgkinson, Mark$^{108}$;

@@

@@

Huang, Xingtao$^{107}$;
Ivanchenko, Vladimir N.$^{5,111}$;
Ivanov, Todor$^{109}$;

@@

Jayatilaka, Bodhitha$^{16,c}$;

@@

Jun, Soon Yung$^{16,c}$;

@@

Kcira, Dorian$^{11}$;

@@

Kirby, Michael$^{16,c}$;

@@

Komarov, Ilya$^{34,n}$;

@@

Kowalkowski, Jim$^{16,c}$;

@@

Kutschke, Robert$^{16,a,c}$;
Kuznetsov, Valentin$^{12}$;

@@

Lewendel, Birgit$^{13}$;

@@

Lima, Guilherme$^{16}$;

@@

Linden, Tomas$^{18}$;

@@

Magini, Nicolò$^{28}$;

@@

Menasce, Dario$^{29,a}$;

@@

Michelotto, Michele$^{32}$;

@@

Morgan, Ben$^{114}$;

@@

Murray, Sean$^{75,10}$;

@@

@@

Oyanguren, Arantza$^{22}$;
Ozturk, Nurcan$^{110}$;
Pacheco Pages, Andres$^{57,20,j}$;
Paganini, Michela$^{116}$;

@@

Pascuzzi, Vincent R.$^{112}$;

@@

Pedro, Kevin$^{16,c}$;
Perdue, Gabriel$^{16}$;
Perez-Calero Yzquierdo, Antonio$^{57,7,g}$;
Perrozzi, Luca$^{15}$;

@@

Piedra, Jónatan$^{21}$;
Piilonen, Leo$^{118,i}$;

@@

Potamianos, Karolos$^{13}$;
Psihas, Fernanda$^{24}$;

@@

Reuter, Jürgen$^{13}$;

@@

Rinaldi, Lorenzo$^{25}$;

@@

Robinson, James$^{13}$;

@@

@@

Sexton-Kennedy, Elizabeth$^{16,a,c}$;

@@

@@

Siroli, Gian Piero$^{25}$;

@@

Stadie, Hartmut$^{17}$;
Stark, Giordon$^{6}$;

@@

Sánchez, Arturo$^{113,19}$;
Sánchez-Hernández, Alberto$^{8,o}$;

@@

@@

Tunnell, Christopher$^{6}$;
Vaandering, Eric$^{16,c}$;

@@

Vlimant, Jean-Roch$^{11,a}$;
Voss, Christian$^{13}$;
Vuosalo, Carl$^{115}$;

@@

@@

Wissing, Christoph$^{13}$;

@@

Xiaomei, Zhang$^{23}$;

@@

Yazgan, Efe$^{23}$

@@

\par {\footnotesize $^{1}$ High Energy Physics Division, Argonne National Laboratory, Argonne IL, USA}
\par {\footnotesize $^{2}$ Physics Department, Brookhaven National Laboratory, Upton NY, USA}

@@

\par {\footnotesize $^{6}$ Enrico Fermi Institute, University of Chicago, Chicago IL, USA}
\par {\footnotesize $^{7}$ Centro de Investigaciones Energéticas Medioambientales y Tecnológicas (CIEMAT), Madrid, Spain}
\par {\footnotesize $^{8}$ Cinvestav, Mexico City, Mexico}
\par {\footnotesize $^{9}$ Centro Nazionale Analisi Fotogrammi (CNAF), INFN, Bologna, Italy}
\par {\footnotesize $^{10}$ Center for High Performance Computing, Cape Town, South Africa}
\par {\footnotesize $^{11}$ California Institute of Technology, Pasadena, California, USA}
\par {\footnotesize $^{12}$ Cornell University, Ithaca, USA}
\par {\footnotesize $^{13}$ Deutsches Elektronen-Synchrotron, Hamburg, Germany}
\par {\footnotesize $^{14}$ Institute of Physics, École Polytechnique Fédérale de Lausanne (EPFL), Lausanne, Switzerland}
\par {\footnotesize $^{15}$ ETH Zurich - Institute for Particle Physics and Astrophysics (IPA), Zurich, Switzerland}
\par {\footnotesize $^{16}$ Fermi National Accelerator Laboratory, Batavia, USA}
\par {\footnotesize $^{17}$ University of Hamburg, Hamburg, Germany}
\par {\footnotesize $^{18}$ Helsinki Institute of Physics, Helsinki, Finland}
\par {\footnotesize $^{19}$ International Center for Theoretical Physics, Trieste, Italy}
\par {\footnotesize $^{20}$ Institut de Física d’Altes Energies and Departament de Física de la Universitat Autònoma de Barcelona and ICREA, Barcelona, Spain}
\par {\footnotesize $^{21}$ Instituto de Física de Cantabria (IFCA), CSIC-Universidad de Cantabria, Santander, Spain}
\par {\footnotesize $^{22}$ Instituto de Física Corpuscular, Centro Mixto Universidad de Valencia - CSIC, Valencia, Spain}
\par {\footnotesize $^{23}$ Institute of High Energy Physics, Chinese Academy of Sciences, Beijing}
\par {\footnotesize $^{24}$ Department of Physics, Indiana University, Bloomington IN, USA}
\par {\footnotesize $^{25}$ INFN Sezione di Bologna, Università di Bologna, Bologna, Italy}
\par {\footnotesize $^{26}$ INFN Sezione di Bari, Università di Bari, Politecnico di Bari, Bari, Italy}
\par {\footnotesize $^{27}$ Università e INFN, Ferrara, Ferrara, Italy}
\par {\footnotesize $^{28}$ INFN Sezione di Genova, Genova, Italy}
\par {\footnotesize $^{29}$ INFN Sezione di Milano-Bicocca, Milano, Italy}
\par {\footnotesize $^{30}$ INFN Sezione di Napoli, Università di Napoli, Napoli, Italy}
\par {\footnotesize $^{31}$ INFN Sezione di Pisa, Università di Pisa, Scuola Normale Superiore di Pisa, Pisa, Italy}
\par {\footnotesize $^{32}$ INFN Sezione di Padova, Università di Padova b, Padova, Italy}
\par {\footnotesize $^{33}$ INFN Sezione di Roma I, Università La Sapienza, Roma, Italy}
\par {\footnotesize $^{34}$ INFN Sezione di Trieste, Università di Trieste, Trieste, Italy}

@@

\par {\footnotesize $^{38}$ Thomas Jefferson National Accelerator Facility, Newport News, Virginia, USA}

@@

\par {\footnotesize $^{44}$ Lawrence Berkeley National Laboratory and University of California, Berkeley CA, USA}

@@

\par {\footnotesize $^{56}$ Center for High Energy Physics, University of Oregon, Eugene OR, USA}

@@

\par {\footnotesize $^{61}$ SLAC National Accelerator Laboratory, Menlo Park CA, USA}
\par {\footnotesize $^{62}$ Simons Foundation, New York, USA}

@@

\par {\footnotesize $^{73}$ University of California, San Diego, La Jolla, USA}

@@

\par {\footnotesize $^{77}$ University of Illinois Urbana-Champaign, Champaign, Illinois, USA}

@@

\par {\footnotesize $^{86}$ Department of Physics and Astronomy, University of Kentucky, Lexington, USA}

@@

\par {\footnotesize $^{94}$ University of Nebraska-Lincoln, Lincoln, USA}
\par {\footnotesize $^{95}$ Department of Physics and Astronomy, University of New Mexico, Albuquerque NM, USA}
\par {\footnotesize $^{96}$ University of Notre Dame, Notre Dame, USA}
\par {\footnotesize $^{97}$ Homer L. Dodge Department of Physics and Astronomy, University of Oklahoma, Norman OK, USA}
\par {\footnotesize $^{98}$ The Ohio State University, Columbus, USA}

@@

\par {\footnotesize $^{103}$ Princeton University, Princeton, USA}

@@

\par {\footnotesize $^{107}$ School of Physics, Shandong University, Shandong, China}
\par {\footnotesize $^{108}$ Department of Physics and Astronomy, University of Sheffield, Sheffield, United Kingdom}
\par {\footnotesize $^{109}$ University of Sofia, Sofia, Bulgaria}
\par {\footnotesize $^{110}$ Department of Physics, The University of Texas at Arlington, Arlington, TX, USA}
\par {\footnotesize $^{111}$ National Research Tomsk Polytechnic University, Tomsk, Russia}
\par {\footnotesize $^{112}$ Department of Physics, University of Toronto, Toronto, ON, Canada}
\par {\footnotesize $^{113}$ Dipartimento di Chimica, Fisica e Ambiente, Università di Udine, Udine, Italy}
\par {\footnotesize $^{114}$ Department of Physics, University of Warwick, Coventry, United Kingdom}
\par {\footnotesize $^{115}$ University of Wisconsin - Madison, Madison, WI, USA}
\par {\footnotesize $^{116}$ Department of Physics, Yale University, New Haven, CT, USA}
\par {\footnotesize $^{117}$ IOP and GUST, Vietnam Academy of Science and Technology (VAST), Hanoi, Vietnam}
\par {\footnotesize $^{118}$ Virginia Tech, Blacksburg, Virginia, USA}

>>>>

Anh-Ky, Nguyen$^{119}$;

@@

Bagliesi, Giuseppe$^{30}$;

@@

Banerjee, Sunanda$^{15,c}$;

@@

Bauerdick, Lothar A. T.$^{15,c}$;
Belforte, Stefano$^{33}$;

@@

Boccali, Tommaso$^{30}$;

@@

Bonacorsi, Daniele$^{24}$;

@@

Bozzi, Concezio$^{26}$;

@@

Canal, Philippe$^{15,c}$;

@@

Carlino, Gianpaolo$^{29}$;

@@

Cervantes Villanueva, Javier$^{5}$;

@@

Chen, Gang$^{22}$;

@@

Coles, Jeremy$^{74}$;

@@

Costanzo, Davide$^{109}$;

@@

Cristella, Leonardo$^{25}$;

@@

De, Kaushik$^{111}$;

@@

De Roeck, Albert$^{5}$;
Delgado Peris, Antonio$^{6,g}$;

@@

Di Guida, Salvatore$^{28}$;

@@

Dykstra, Dave$^{15,c}$;

@@

Elvira, V. Daniel$^{15,c}$;

@@

Farrell, Steven$^{44}$;

@@

Fitzpatrick, Conor$^{13}$;
Flix, José$^{57,6,g}$;

@@

Franzoni, Giovanni$^{5}$;

@@

Fuess, Stu$^{15,c}$;
Gaede, Frank$^{12}$;

@@

Gellrich, Andreas$^{12}$;
Genser, Krzysztof$^{15,c}$;

@@

Giacomini, Francesco$^{8}$;
Giagu, Stefano$^{106,32}$;

@@

Glushkov, Ivan$^{111}$;

@@

Govi, Giacomo$^{15}$;
Grandi, Claudio$^{24}$;

@@

Guan, Wen$^{116}$;
Gutsche, Oliver$^{15,c}$;

@@

Hartmann, Thomas$^{12}$;

@@

Heinemann, Beate$^{12}$;

@@

Hernández, José M.$^{6,g}$;

@@

Hodgkinson, Mark$^{109}$;

@@

Holzman, Burt$^{15,c}$;

@@

Huang, Xingtao$^{108}$;
Ivanchenko, Vladimir N.$^{5,112}$;
Ivanov, Todor$^{110}$;

@@

Jayatilaka, Bodhitha$^{15,c}$;

@@

Jun, Soon Yung$^{15,c}$;

@@

Kcira, Dorian$^{10}$;

@@

Kirby, Michael$^{15,c}$;

@@

Komarov, Ilya$^{33,n}$;

@@

Kowalkowski, Jim$^{15,c}$;

@@

Kutschke, Robert$^{15,a,c}$;
Kuznetsov, Valentin$^{11}$;

@@

Lewendel, Birgit$^{12}$;

@@

Lima, Guilherme$^{15,c}$;

@@

Linden, Tomas$^{17}$;

@@

Lyon, Adam$^{15,c}$;
Magini, Nicolò$^{27}$;

@@

Menasce, Dario$^{28,a}$;

@@

Michelotto, Michele$^{31}$;

@@

Morgan, Ben$^{115}$;

@@

Murray, Sean$^{75,9}$;

@@

Norman, Andrew$^{15,c}$;

@@

Oyanguren, Arantza$^{21}$;
Ozturk, Nurcan$^{111}$;
Pacheco Pages, Andres$^{57,19,j}$;
Paganini, Michela$^{117}$;

@@

Pascuzzi, Vincent R.$^{113}$;

@@

Pedro, Kevin$^{15,c}$;
Perdue, Gabriel$^{15,c}$;
Perez-Calero Yzquierdo, Antonio$^{57,6,g}$;
Perrozzi, Luca$^{14}$;

@@

Piedra, Jónatan$^{20}$;
Piilonen, Leo$^{120,i}$;

@@

Potamianos, Karolos$^{12}$;
Psihas, Fernanda$^{23}$;
Puig Navarro, Albert$^{118}$;

@@

Reuter, Jürgen$^{12}$;

@@

Rinaldi, Lorenzo$^{24}$;

@@

Robinson, James$^{12}$;

@@

Rybkine, Grigori$^{43}$;

@@

Sexton-Kennedy, Elizabeth$^{15,a,c}$;

@@

Sgalaberna, Davide$^{5}$;

@@

Siroli, Gian Piero$^{24}$;

@@

Spentzouris, Panagiotis$^{15,c}$;
Stadie, Hartmut$^{16}$;
Stark, Giordon$^{78}$;

@@

Sánchez, Arturo$^{114,18}$;
Sánchez-Hernández, Alberto$^{7,o}$;

@@

Tamponi, Umberto$^{34}$;

@@

Tunnell, Christopher$^{78}$;
Vaandering, Eric$^{15,c}$;

@@

Vlimant, Jean-Roch$^{10,a}$;
Voss, Christian$^{12}$;
Votava, Margaret$^{15,c}$;
Vuosalo, Carl$^{116}$;

@@

Watts, Gordon T$^{107}$;

@@

Wissing, Christoph$^{12}$;

@@

Xiaomei, Zhang$^{22}$;

@@

Yazgan, Efe$^{22}$

@@

\par {\footnotesize $^{1}$ High Energy Physics Division, Argonne National Laboratory, Argonne, IL, USA}
\par {\footnotesize $^{2}$ Physics Department, Brookhaven National Laboratory, Upton, NY, USA}

@@

\par {\footnotesize $^{6}$ Centro de Investigaciones Energéticas Medioambientales y Tecnológicas (CIEMAT), Madrid, Spain}
\par {\footnotesize $^{7}$ Cinvestav, Mexico City, Mexico}
\par {\footnotesize $^{8}$ Centro Nazionale Analisi Fotogrammi (CNAF), INFN, Bologna, Italy}
\par {\footnotesize $^{9}$ Center for High Performance Computing, Cape Town, South Africa}
\par {\footnotesize $^{10}$ California Institute of Technology, Pasadena, California, CA, USA}
\par {\footnotesize $^{11}$ Cornell University, Ithaca, NY, USA}
\par {\footnotesize $^{12}$ Deutsches Elektronen-Synchrotron, Hamburg, Germany}
\par {\footnotesize $^{13}$ Institute of Physics, École Polytechnique Fédérale de Lausanne (EPFL), Lausanne, Switzerland}
\par {\footnotesize $^{14}$ ETH Zürich - Institute for Particle Physics and Astrophysics (IPA), Zürich, Switzerland}
\par {\footnotesize $^{15}$ Fermi National Accelerator Laboratory, Batavia, IL, USA}
\par {\footnotesize $^{16}$ University of Hamburg, Hamburg, Germany}
\par {\footnotesize $^{17}$ Helsinki Institute of Physics, Helsinki, Finland}
\par {\footnotesize $^{18}$ International Center for Theoretical Physics, Trieste, Italy}
\par {\footnotesize $^{19}$ Institut de Física d’Altes Energies and Departament de Física de la Universitat Autònoma de Barcelona and ICREA, Barcelona, Spain}
\par {\footnotesize $^{20}$ Instituto de Física de Cantabria (IFCA), CSIC-Universidad de Cantabria, Santander, Spain}
\par {\footnotesize $^{21}$ Instituto de Física Corpuscular, Centro Mixto Universidad de Valencia - CSIC, Valencia, Spain}
\par {\footnotesize $^{22}$ Institute of High Energy Physics, Chinese Academy of Sciences, Beijing}
\par {\footnotesize $^{23}$ Department of Physics, Indiana University, Bloomington, IN, USA}
\par {\footnotesize $^{24}$ INFN Sezione di Bologna, Università di Bologna, Bologna, Italy}
\par {\footnotesize $^{25}$ INFN Sezione di Bari, Università di Bari, Politecnico di Bari, Bari, Italy}
\par {\footnotesize $^{26}$ Università e INFN, Ferrara, Ferrara, Italy}
\par {\footnotesize $^{27}$ INFN Sezione di Genova, Genova, Italy}
\par {\footnotesize $^{28}$ INFN Sezione di Milano-Bicocca, Milano, Italy}
\par {\footnotesize $^{29}$ INFN Sezione di Napoli, Università di Napoli, Napoli, Italy}
\par {\footnotesize $^{30}$ INFN Sezione di Pisa, Università di Pisa, Scuola Normale Superiore di Pisa, Pisa, Italy}
\par {\footnotesize $^{31}$ INFN Sezione di Padova, Università di Padova b, Padova, Italy}
\par {\footnotesize $^{32}$ INFN Sezione di Roma I, Università La Sapienza, Roma, Italy}
\par {\footnotesize $^{33}$ INFN Sezione di Trieste, Università di Trieste, Trieste, Italy}
\par {\footnotesize $^{34}$ INFN Sezione di Torino, Torino, Italy}

@@

\par {\footnotesize $^{38}$ Thomas Jefferson National Accelerator Facility, Newport News, Virginia, VA, USA}

@@

\par {\footnotesize $^{44}$ Lawrence Berkeley National Laboratory and University of California, Berkeley, CA, USA}

@@

\par {\footnotesize $^{56}$ Center for High Energy Physics, University of Oregon, Eugene, OR, USA}

@@

\par {\footnotesize $^{61}$ SLAC National Accelerator Laboratory, Menlo Park, CA, USA}
\par {\footnotesize $^{62}$ Simons Foundation, New York, NY, USA}

@@

\par {\footnotesize $^{73}$ University of California, San Diego, La Jolla, CA, USA}

@@

\par {\footnotesize $^{77}$ University of Illinois Urbana-Champaign, Champaign, Illinois, IL, USA}

@@

\par {\footnotesize $^{86}$ Department of Physics and Astronomy, University of Kentucky, Lexington, KY, USA}

@@

\par {\footnotesize $^{94}$ University of Nebraska-Lincoln, Lincoln, NE, USA}
\par {\footnotesize $^{95}$ Department of Physics and Astronomy, University of New Mexico, Albuquerque, NM, USA}
\par {\footnotesize $^{96}$ University of Notre Dame, Notre Dame, IN, USA}
\par {\footnotesize $^{97}$ Homer L. Dodge Department of Physics and Astronomy, University of Oklahoma, Norman, OK, USA}
\par {\footnotesize $^{98}$ The Ohio State University, Columbus, OH, USA}

@@

\par {\footnotesize $^{103}$ Princeton University, Princeton, NJ, USA}

@@

\par {\footnotesize $^{107}$ University of Washington, Seattle, WA, USA}
\par {\footnotesize $^{108}$ School of Physics, Shandong University, Shandong, China}
\par {\footnotesize $^{109}$ Department of Physics and Astronomy, University of Sheffield, Sheffield, United Kingdom}
\par {\footnotesize $^{110}$ University of Sofia, Sofia, Bulgaria}
\par {\footnotesize $^{111}$ Department of Physics, The University of Texas at Arlington, Arlington, TX, USA}
\par {\footnotesize $^{112}$ National Research Tomsk Polytechnic University, Tomsk, Russia}
\par {\footnotesize $^{113}$ Department of Physics, University of Toronto, Toronto, ON, Canada}
\par {\footnotesize $^{114}$ Dipartimento di Chimica, Fisica e Ambiente, Università di Udine, Udine, Italy}
\par {\footnotesize $^{115}$ Department of Physics, University of Warwick, Coventry, United Kingdom}
\par {\footnotesize $^{116}$ University of Wisconsin - Madison, Madison, WI, USA}
\par {\footnotesize $^{117}$ Department of Physics, Yale University, New Haven, CT, USA}
\par {\footnotesize $^{118}$ Physik-Institut, Universität Zürich, Zürich, Switzerland}
\par {\footnotesize $^{119}$ IOP and GUST, Vietnam Academy of Science and Technology (VAST), Hanoi, Vietnam}
\par {\footnotesize $^{120}$ Virginia Tech, Blacksburg, Virginia, VA, USA}
